\section{Summary}
\label{sec:conclusions}

In this work, a new determination of the photon PDF from
a fit of HERA inclusive DIS structure functions supplemented
by ATLAS data on high-mass Drell-Yan cross
sections has been presented, based on the {\tt xFitter} framework.
%
As suggested by a previous reweighting analysis~\cite{Aad:2016zzw}, this
high-mass DY data provides significant constraints on the photon PDF,
allowing a determination of $x\gamma(x)$ with uncertainties at the
30\% level for $0.02 \le x \le 0.1$, which then increase for higher
values of $x$.
%
The results of the present study, dubbed {\tt xFitter\_epHMDY}, are in agreement
and exhibit smaller PDF uncertainties that the only
other existing photon PDF fit from LHC data, the 
NNPDF3.0QED analysis, based on older LHC Drell-Yan measurements.

Our results are in agreement within uncertainties with two recent
calculations of the photon PDF, LUXqed and HKR16, in the region of $x$
where the ATLAS DY data has sensitivity.
%
For $x\ge 0.1$, the agreement is at the 1-$\sigma$ level already including
only the experimental MC uncertainties, while for $0.02 \ge x \ge 0.1$ it is
important to account as well for the parametrization uncertainties.
%
Our findings indicate that a direct determination of the
photon PDF from hadron collider data
is still far from being competitive with the LUXqed and HKR
calculations, which are based instead on precise measurements of the inclusive DIS
structure functions of the proton.
%
However, the {\tt xFitter\_epHMDY} analysis provides further evidence that the information
on the photon PDF provided by the most sensitive LHC data available so far
is fully consistent with these two independent calculations.

The results of this study, which
 are available upon
 request in the {\tt LHAPDF6} format~\cite{Buckley:2014ana},
 have been made possible by a number of
technical developments that should be of direct application for future
PDF fits accounting for QED corrections.
%
First of all, the full NLO
QED corrections to the DGLAP evolution equations and the DIS
structure functions have been implemented in the  {\tt APFEL} program.
%
Moreover, our results illustrate the flexibility of the {\tt
  xFitter} framework to extend its capabilities beyond the traditional
quark and gluon PDF fits.
%
Finally, the extension of {\tt aMCfast} and {\tt APPLgrid} to allow
for the presence of photon-initiated channels in the calculations
provided by {\tt MadGraph5\_aMC@NLO}, significantly streamlines the
inclusion of future LHC measurements in PDF fits with QED corrections by
consistently including diagrams with initial-state photons.
%
All these technical improvements will certainly be helpful for future
studies of the photon content of the proton.\\

{\bf Acknowledgments}.
%
We thank L.~Harland-Lang for providing us the {\tt LHAPDF6} grid of
the HKR16 photon determination.
%
We thank A.~Sapronov for providing support to the {\tt xFitter} platform.
%
%We thank R.~Sadykov for early cross checks of the QED evolution program in {\tt xFitter}.
%
We thank P.~Starovoitov for discussions related to the {\tt APPLgrid} files.
%
We thank M.~Zinser for discussions related to the ATLAS data.
% 
We thank M.~Dyndal for discussions on the scale choices for the photon induced contributions.
%
The work of V.~B., F.~G., J.~R. has been supported by the European
Research Council Starting Grant ``PDF4BSM".
%
V.~R. acknowledges support from the Department of Physics at the University of
Oxford, where part of this work was completed.
%
The work of R.~S. and P.~S. has been supported in part by Helmholtz Gemeinschaft
under contract VH-HA-101, BMBF-JINR cooperation and Heisenberg-Landau programs.
%
We are grateful to the DESY IT department for their support of the {\tt xFitter} developers. 



